---
title: "W_UP_01"
author: "Thomas Matthews"
date: "Spring 2021"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players.

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->
I am using two main methods; the first one is Graphical Descriptive Results 2. Visual Data set. 
# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results
The results indicate that skill players are able to do more pushups than the line players. The skill players are able to do 54 pushups and the line players are able to do 20 pushups. 
### Graphical Descriptive Results
the skill player with the most pushups was 108 and the the line player with the most pushups was 34. 
<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
basicCN <- ggplot(mydata,aes(x=position,y=pushups))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Skill vs line pushups")
```
### Numerical Descriptive Results
```{r}
favstats(pushups~position,data=mydata)
```

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
The numerical results indicate that skill players beat line players. The general mean from the numerical description above show that skill players do around 49.72727 pushups and line players do about 17.12500 pushups. 
## Inferential Results
```{r}
t.test(pushups~position,data=mydata)
```
<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
 My hypothese is that skill players will beat the line players. The plot shows skill players do around 54 pushups and line players do only 20. 

# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
Skilled players are able to do more pushups than the line players because they are smaller and weigh less whereas line players might be heavier and unabel to life their body weight. 
